\chapter*{Abstract}
\noindent 
\vspace{10mm}
\normalsize

A search for new physics with a signature of missing energy in events with high \Pt jets is presented. The analysis is performed with 1.1fb$^{-1}$ of 7~TeV data taken using the Compact Muon Solenoid detector at the Large Hadron Collider in 2011. The kinematic variable \alt is used to control the dominant QCD background that exhibits fake missing energy originating from mismeasurment. The remaining electroweak backgrounds are estimated using data-driven techniques through the use of two control samples. The background from boosted W decays is estimated with the use of a dedicated $\mu$ + jets control sample, while the irreducible background from Z $\ra \nu \bar{\nu}$ is estimated using a $\gamma$ + jets control sample.  A shape analysis is performed across eight bins in \HT, with the signal selection and the two control samples treated simultaneously in a likelihood fit.  The data was found to agree very well with the Standard Model only hypothesis with a p-value of 0.56, which indicates no evidence of new physics. The results are interpreted in the scope of a possible new physics model, the Constrained Minimal Supersymmetric Standard Model. Exclusion limits are set at the 95\% confidence level on the parameters m$_{0}$ and m$_{1/2}$ that set the mass hierarchies of the sparticles. An extension is also presented allowing additional signal into the muon control sample. The effect on the limit is negligible, although adopting a leptonic variable of the \alt variable increases the ratio between signal and background events significantly. This approach is recommended for searches with higher statistics in 2012. 



