\chapter*{Acknowledgements}

%\noindent

\normalsize

I would like to extend my thanks to everyone who worked with me and helped me in the course of this Ph.D. I am sincerely and heartily grateful to my advisor, Jordan Nash, for the support and guidance he showed me throughout my time at Imperial College.

It has been a pleasure to be a member of the Imperial RA1 team alongside Rob Bainbridge, Burt Betchart, Oliver Buchm\"uller, Darren Burton, Edward Laird, Bryn Mathias, Henning Fl\"acher, Tanja Rommerskirchen, Paris Sphicas, Markus Stoye, and Tom Whyntie. It would also not have been possible without Georgia Karapostoli, for teaching me so much in the beginning. 

My heart goes out to everyone I met at CERN, and who made my time there so special. To all the wonderful UK LTA crew who are too numerous to name individually. Collectively you made my time at CERN the best time of my life and I one I will never forget. I had a wonderful two and a half years and had a lot of new and exciting experiences. I will miss you all so much. Special thanks to the LTA ladies for girly nights full of gossip and great food/wine/company! 

I am indebted to my flatmate, Amin, for offering me a place to stay when I had almost given up and for keeping me sane throughout my final stay in London. 

Many many thanks to my parents, Jan and Adrian, who have supported me through everything I have been through for my whole life. You taught me that anything I want in life is within my grasp. Thanks for always believing in me and being there when the times were toughest. I am indebted to my mother for proofreading not only this thesis, but everything I have ever written.  

Last, but definitely not least, I want to say a special thanks to Chris for all the love and support. Without you I would not have made it though this difficult time, and I will always be grateful for your patience and help. My days as a student have come to an end, but you fill my future with hope. 

