\chapter{Extending the $\mu$ Control Sample to a Signal Sample}

In Chapter~\ref{ch:RA1}, the $\mu$ control sample was used effectively to predict the background contribution from W and \tto events. The $\mu$ likelihood's incorporation into the overall likelihood in order to interpret the hadronic results allowed for some small signal contamination. However it was in general viewed as a constraint on the ``signal" region of the hadronic selection. 

The cuts outlined in Section~\ref{sec:musel} are designed to select events from Standard Model W decays, hence minimising the contamination from signal. However, as the simultaneous fit includes the signal efficiency in the $\mu$ control sample it is possible to relax the cuts and allow more potential signal into the $\mu$ yield. The following work represents the author's personal investigation into the effect of increasing the chance for signal contamination on the eventual limit. 

\subsection{Relaxing the Cuts}

The primary cut in the $\mu$ control sample responsible for restricting the signal is the M$_{T}$ requirement, as it puts a restriction on boosted W decays. The first step is to remove this cut. Having done so there are three possible scenarios with respect to the \alt cut

\begin{itemize}
\item Use the \alt cut from the hadronic analysis, where the muon is ignored
\item Take out the \alt cut to increase statistics in the $\mu$ sample (the MHT/HT cut ensures the elimination of QCD background)
\item Adapt the definition of the \alt to include the lepton, the validity of which is shown in Section~\ref{sec:lepalt}
\end{itemize}

The one muon requirement cuts remain 

\subsection{Event Yields}
\subsection{Fit Results}





\begin{table}[htbp]
\centering
\footnotesize
\begin{tabular*}{0.99\linewidth}{@{\extracolsep{\fill}}c c c c c c}
\hline
\hline
& \scalht Bin (GeV) & 275--325 & 325--375 & 375--475 & 475--575 \\ [0.5ex]
\hline
\hline
\multirow{3}{*}{2011 Selection} & B (SM) &407.5 & 179.1  & 131.6 & 48.7 \\
&S (LM6)&0.15 & 0.15 & 0.53 & 0.82\\
& S / B & 0.000 & 0.001 & 0.004 & 0.017\\
\hline
\multirow{3}{*}{No M$_{T}$ Cut \& \alt $>$ 0.55} & B (SM) &549.93 &243.33&179.51 &63.80 \\
&S (LM6)& 0.19 & 0.20 & 0.59 & 0.92 \\
& S/B & 0.000 & 0.001 & 0.003 & 0.0014 \\
\hline
\multirow{3}{*}{No M$_{T}$ Cut \& \alt$_{lep}$ $>$ 0.55} & B (SM) & 163.95 & 70.64 & 39.87  & 16.38  \\
& S (LM6) & 0.13 & 0.17 & 0.51 & 0.79 \\
& S/B & 0.001 & 0.002 & 0.013 & 0.048 \\
\hline
\multirow{3}{*}{No M$_{T}$ Cut \& No \alt} & B (SM) &1335.81& 603.61 & 485.62 & 192.61\\
&S (LM6) &0.26&0.32&0.89&1.43\\
& S/B & 0.000 & 0.001 & 0.002 & 0.007 \\
\hline
\hline
\end{tabular*}
\newline
\newline
\newline
\begin{tabular*}{0.99\linewidth}{@{\extracolsep{\fill}}c c c c c c}
\hline
\hline
& \scalht Bin (GeV) & 575--675 & 675--775 & 775--875 & 875--$\infty$  \\ [0.5ex]
\hline
\hline

\multirow{3}{*}{2011 Selection} & B (SM) &13.32  & 7.95  & 3.20 & 0.97 \\
&S (LM6)&1.09 & 1.17 & 0.95 & 1.21\\
& S / B & 0.082 & 0.147 & 0.297 & 1.343\\
\hline
\multirow{3}{*}{No M$_{T}$ Cut \& \alt $>$ 0.55} & B (SM) & 18.53 & 8.59 & 3.34 & 0.97 \\
&S (LM6)& 1.23 & 1.35 & 1.08 & 1.42 \\
& S/B & 0.066 & 0.157 & 0.324 & 1.5747 \\
\hline
\multirow{3}{*}{No M$_{T}$ Cut \& \alt$_{lep}$ $>$ 0.55} & B (SM) & 7.85 & 1.76 & 0.05 & 0.05  \\
& S (LM6) & 1.05 & 1.13 & 0.89 & 1.06 \\
& S/B & 0.134 & 0.641 & 19.282 & 22.982 \\
\hline
\multirow{3}{*}{No M$_{T}$ Cut \& No \alt} & B (SM) & 67.64 & 30.04 & 12.77 & 3.26 \\
&S (LM6) &1.87 & 2.04 & 1.77 & 3.07\\
& S/B & 0.028 & 0.068 & 0.139 & 0.940 \\
\hline
\hline
\end{tabular*}
\end{table}


