\documentclass[a4, 10pt]{cmspaper}

%\usepackage{multirow}
%\usepackage{subfigure}
%\usepackage{subfig}

\usepackage[pdftex]{graphicx}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{array}% in the preamble

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\nn}{\nonumber}
\newcommand{\dsn}{\displaystyle{\not}}

\begin{document}

%==============================================================================
% title page for few authors

\begin{titlepage}

% select one of the following and type in the proper number:
%  \internalnote{2009/000}
%  \conferencereport{2005/000}
   \date{\today}

 \title{Performance of QCD background estimation methods for single lepton SUSY searches}

 \begin{Authlist}
   O.~Buchmueller\Aref{a}, Z.~Hatherell\Aref{a}, G.~Karapostoli\Aref{a}, A.~Sparrow\Aref{a}, P.~Sphicas\Aref{b,c},
	A.~Tapper\Aref{a}
       \Instfoot{ic}{a) Imperial College London, United Kingdom}	
     \Instfoot{cern}{b) CERN, Geneva, Switzerland}	
\Instfoot{uoa}{c) University of Athens, Greece}
   \end{Authlist}

\begin{abstract}
The performance of data-driven QCD background estimation methods to be used for single lepton SUSY searches is studied. The methods are contructed using Monte Carlo datasets, and the performance is studied with an X $pb^{-1}$ sample of 7 TeV LHC collisions. The data provides many events with one electron and at least one jet, with which we validate the method of predicting the disibution of the $\alpha_{T}$ jet-balancing kinematic variable. This is undertaken by inverting the cuts on $\Delta \phi$ and $\Delta \eta$ Electron ID variables. Another method utilises Isolation templates in control regions to predict the distribution in the signal region. 
\end{abstract}


\end{titlepage}

\tableofcontents
\newpage
\setcounter{page}{2}
\input{Intro}



%\newpage
\input{EventSel}


%\clearpage

\input{QCD_bkgd_est-v3}

%\clearpage

%\newpage
\input{comiss}

\input{summary}
\clearpage

\begin{thebibliography}{9}
%\bibitem{lisa}{L.~Randall and D.~Tucker-Smith, {\em``Dijet searches for Supersymmetry at the LHC''}, Phys. Rev. Lett. \bf{101} (2008) 221803, arXiv:0806.1049.}
\bibitem{data}{https://twiki.cern.ch/twiki/bin/view/CMS/ProductionSummer2009.}
\bibitem{mad}{J~Alwall et al., ``MadGraph/MadEvent v4: The New Web generation'', JHEP 09 (2007) 028, arXiv:0706.2334.}
\bibitem{susypat1} {https://twiki.cern.ch/twiki/bin/view/CMS/SusyPat.}
\bibitem{susypat2} {https://twiki.cern.ch/twiki/bin/view/CMS/SWGuidePAT.}
\bibitem{susypat}{https://twiki.cern.ch/twiki/bin/view/CMS/SusyPatLayer1.}
\bibitem{ICNT}{https://twiki.cern.ch/twiki/bin/view/CMS/SusyCAFNtupleV000804XX.}
\bibitem{PDWG}{https://twiki.cern.ch/twiki/bin/view/CMS/PhysicsSecondaryDatasets.}
\bibitem{elsel}{https://twiki.cern.ch/twiki/bin/view/CMS/SimpleCutBasedEleID.}
\bibitem{conv}{https://twiki.cern.ch/twiki/bin/view/CMS/ConversionBackgroundRejection.}
\bibitem{cornel}{L.~Agostino, A.~Chatterjee, R.~Patterson, D.~Puigh, W.~Sun, J.~Thom, J.~Vaughan, P.~Wittich, ``Estimation of Fake Electron background using Data-Driven Techniques'', CMS Analysis Note 2010/043.}
\bibitem{elecid}{J.~Branson, M.~Gallinaro, P.~Ribeiro, R.~Salerno, M.~Sani, ```A cut based method for electron identification in CMS'', CMS Analysis Note 2008/082.}
\bibitem{njet}{H.~Flaecher, M.~Stoye, T.~Rommerskirchen, T.~Yetkin, T.~Whyntie, R.~Bainbridge, J.~Marrouche, {\em``Search for SUSY with exclusive n-jet events''}, CMS Analysis Note 2008/082. }
\bibitem{ouratnote}{O.~Buchmueller, L.~Gouskos, Z.~Hatherell, G.~Karapostoli, A.~Sparrow, P.~Sphicas, ``An application of the $\alpha_{T}$ jet-balancing method to the single-lepton mode SUSY searches,'' CMS Analysis Note 2009/188.}
\bibitem{david}{Paul Geffert and David Stuart, ``Study of the Correlation between $\alpha_{T}$ and $H_{T}$ using Z+jets events'', CMS Analysis Note 2009/155.}



\end{thebibliography}

\end{document}
